Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
Removing todos.

\todo[inline]{Security. How to prevent a group of people to vote and by trick reaching statistical quorum.
We use dynamic statistical quorum to address this, but one other approach is also for voting to stay open and
decisions can then be in the future revoked by people adding more votes, or changing them. But for some decisions
this might not really be possible, because decisions might not be reversible. You can revoke a law, but if you built
a building as a consequence of a decision?\\
(See near/post-quorum validation phase idea in GitHub issues as one suggested solution.)}

\todo[inline]{Discuss how this might or might not lead to a more inclusive decision making: some people prefer it because
they have time to collect thoughts and can participate when they have time, some people do not because they feel
they cannot communicate as effectively, especially with lack of emotions being conveyed.}

>>>>

%\todo[inline]{Security. How to prevent a group of people to vote and by trick reaching statistical quorum.
%We use dynamic statistical quorum to address this, but one other approach is also for voting to stay open and
%decisions can then be in the future revoked by people adding more votes, or changing them. But for some decisions
%this might not really be possible, because decisions might not be reversible. You can revoke a law, but if you built
%a building as a consequence of a decision?\\
%(See near/post-quorum validation phase idea in GitHub issues as one suggested solution.)}

%\todo[inline]{From interviews: Discuss how this might or might not lead to a more inclusive decision making: some people prefer it because
%they have time to collect thoughts and can participate when they have time, some people do not because they feel
%they cannot communicate as effectively, especially with lack of emotions being conveyed.}
